### 2024-05-22 getting-started.qmd
20240522 - try loading git lfs data file
Revert "20240522 - try loading git lfs data file"
This reverts commit 0e8f950bb10689b76cc914bd41f072854e3f9aeb.

nfl_pbp <- nflfastR::load_pbp(seasons = TRUE)
```

@@

load(file = here("data", "nfl_pbp.RData"))
```

@@

@@

@@

>>>>

```{r}
nfl_pbp <- nflfastR::load_pbp(seasons = TRUE)
```

@@

@@

load(file = here("data", "nfl_actualStats_weekly.RData"))
```

@@

load(file = here("data", "nfl_actualStats_career.RData"))
```

@@

load(file = here("data", "nfl_actualStats_seasonal.RData"))
```
